---
title: "The Office"
author: "Andy"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Get the Data
office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')
```

# Use office_ratings to plot the IMDB ratings by Season. Plot each Season separately (hint, use facet_wrap(.~season)) with each episode plotted on its season's graph.

```{r echo=FALSE, message=FALSE, warning=FALSE}

office_ratings %>%
  mutate(new_season = paste("Season", season, sep = " "))



# Plot data here
library(plotly)
library(tidyverse)

p = office_ratings %>%
  mutate(new_season = paste("Season", season, sep = " ")) %>%
  ggplot(aes(x = episode, y = imdb_rating)) +
  geom_line(group = 1) +
  geom_point() +
  theme_light() +
  facet_wrap(~new_season)

ggplotly(p)
```

# Get average IMDB ratings for each season, including SD and SE

```{r}
# Get average per season here
```

# Plot average season ratings on one graph. Include error bars with SE. Make sure the title is centered and axes are labeled. 

```{r}
# Plot average season ratings here
```

# Run an analysis to determine if there is a main effect of season, or trend (e.g. later season get higher ratings i.e. the show gets better)

```{r}
# Run your analysis here
```

